Convolutional Neural Networks and Volcano Plots: Screening and Prediction of Two-Dimensional Single-Atom Catalysts for CO\textsubscript{2} Reduction Reactions

### 2024-01-14 paper/arxiv/supp_3_ml.tex
adjust table spaces
make subfig label bold

% SI Figure 18: d-band venter vs adsorption energy scatter plot
\begin{figure}[htbp]
  \centering
  \includegraphics[width=\textwidth]{supp_fig18_d-band_eads.png}
  \caption{\textbf{Scatter plot of d-Band Center and Adsorption Energy Relationships.}
  This figure delineates the relationship between d-band center and adsorption energies for
  various species: (a) CO\textsubscript{2}, (b) COOH, (c) CO, (d) CHO,
  (e) CH\textsubscript{2}O, (f) OCH\textsubscript{3}, (g) O, and (h) OH.
  Data from all six substrates investigated in this study are included.}
  \label{supp_fig18:dband_vs_eads}
\end{figure}

>>>>

% SI Figure 18: d-band venter vs adsorption energy scatter plot
\begin{figure}[htbp]
  \centering
  \includegraphics[width=\textwidth]{supp_fig18_d-band_eads.png}
  \caption{\textbf{Scatter plot of d-Band Center and Adsorption Energy Relationships.}
  This figure delineates the relationship between d-band center and adsorption energies for
  various species: (\textbf{a}) CO\textsubscript{2}, (\textbf{b}) COOH, (\textbf{c}) CO,
  (\textbf{d}) CHO, (\textbf{e}) CH\textsubscript{2}O, (\textbf{f}) OCH\textsubscript{3},
  (\textbf{g}) O, and (\textbf{h}) OH.
  Data from all six substrates investigated in this study are included.}
  \label{supp_fig18:dband_vs_eads}
\end{figure}
